---
title: "Boots for Days!"
author: "Lillian Holden"
date: "Final Homework Due November 22nd by 5PM"
output: rmdformats::readthedown
---

### Use library() to access the following packages: 
```{r message=FALSE, warning=FALSE}
library(curl)
library(boot)
```

## Part One 

### Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).


### Import the Data Set

```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall23/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE) #Assign D as the vector for the data set
head(d)
```

### Determine the Intercept/Slope Coefficients by Calling the Information

```{r}
mI <-  lm(log(HomeRange_km2) ~ log(Body_mass_female_mean), data = d)
summary(mI) #calling information to get the intercept and the slope
confint(mI) #finding the CIs by calling them
```
The Slope of This Linear Regression is 1.036, and the intercept is -9.441. 


## Part Two 

### Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.


```{r}
set.seed(1)

#define function to calculate fitted regression coefficients
coef_function <- function(formula, data, indices) {
  newdata <- data[indices,] #allows boot to select sample
  fit <- lm(formula, data=newdata) #fit regression model
  return(coef(fit)) #return coefficient estimates of model
}

#perform bootstrapping with 1000 replications
reps <- boot(data=d, statistic=coef_function, R=1000, formula=log(HomeRange_km2) ~ log(Body_mass_female_mean))

#view results of boostrapping
reps

```
### Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.

```{r}
boot.ci(reps, type="bca", index=1) #intercept of model
boot.ci(reps, type="bca", index=2) #slope of model
```
### Answer the following questions:


#### How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?
The SE for the intercept of the lm model is 0.67. The SE for the intercept of the bootstrapping model is 0.62. The SE for the slope of the lm model is 0.085. The SE for the intercept of the bootstrapping model is 0.079. 
The SE for the intercept coeffiient and slope for the lm model and bootstrapping model are very similar. 


#### How does the latter compare to the 95% CI estimated from your entire dataset?
The CIs for the intercept of the lm model are -10.77 and -8.11. The CIs for the intercept of the bootstrapping model are -10.80, and -8.36. The CIs for the slope of the lm model are 0.87 and 1.20. The CIs for the intercept of the bootstrapping model are 0.89 and 1.21. Both CIs for the intercept and slope coefficient of the lm model and bootstrapping are quite similar. 

Information for Part 2 was found at https://www.statology.org/bootstrapping-in-r/
